\documentclass{beamer}

\title{Git is awesome!}
\author{Florian Biermann\\\texttt{fbie@itu.dk}}
\institute{Pit Lab\\IT University of Copenhagen}

\begin{document}
\frame{\titlepage}

\begin{frame}{Why would you even use Git?}

  \begin{itemize}
  \item It's so complicated.
  \item Just push, or commit, or whatever.
  \item Hah, now it broke again, see?
  \end{itemize}

\end{frame}

\begin{frame}{What's the idea behind Git?}

  \begin{itemize}
  \item A distributed versioning system for text and binary files.
  \item There is no single, monolithic repository: everyone has their own copy of it!
  \item Fine-grained control of what goes into the index and when.
  \item Very well suited for continuous integration with build servers.
  \item Used for documentation of large projects, subject to research, or just to mange your thesis.
  \end{itemize}

\end{frame}

\begin{frame}{A quick outline}

  \begin{itemize}
  \item Getting an overview
    \begin{itemize}
    \item \texttt{git clone} and \texttt{git status}
    \item \texttt{git diff} and \texttt{git log}
    \end{itemize}
  \item Editing the index
    \begin{itemize}
    \item \texttt{git commit} and \texttt{git push}
    \item \texttt{git pull} and \texttt{git fetch}
    \end{itemize}
  \item Reparing things
    \begin{itemize}
    \item \texttt{git checkout}
    \item \texttt{git revert} and \texttt{git reset}
    \end{itemize}
  \item Branches and fancy stuff
    \begin{itemize}
    \item \texttt{git branch}
    \item \texttt{git merge} and \texttt{git rebase}
    \end{itemize}
  \item Maybe some extras, if time permits
    \begin{itemize}
    \item \texttt{git bisect}
    \item The \texttt{.gitignore} file
    \end{itemize}
  \end{itemize}

\end{frame}

\begin{frame}{Some Do's and Dont's}

  \begin{itemize}
  \item By convention, use imperative form for commit messages.
    \begin{itemize}
    \item \textbf{Wrong}
      \begin{itemize}
      \item ``Added a new function foo()''
      \item ``Rearranged methods section''
      \end{itemize}
    \item \textbf{Right}
      \begin{itemize}
      \item ``Add a new function foo()''
      \item ``Rearrange methods section''
      \end{itemize}
    \end{itemize}
  \item If your commit message is really long, use two newlines to
    split it up into overview and detailed description.
  \item Always perform functional and layout changes in separate
    commits.
  \item Do not use \texttt{git push -f} unless you \textbf{really}
    know what you're doing.
  \end{itemize}

\end{frame}

\begin{frame}{Some resources on the net}

  \begin{itemize}
  \item \url{http://git-scm.com/} \\Official website, lots of
    documentation etc.
  \item \url{http://jwiegley.github.io/git-from-the-bottom-up/} \\A
    really detailed, from the bottom up, approach to Git.
  \item \url{http://training.github.com/kit/downloads/github-git-cheat-sheet.pdf}
    \\What everyone really wants: a Git cheat sheet.
  \end{itemize}
\end{frame}

\begin{frame}{Thanks for listening!}

  \center{Any questions?}

\end{frame}

\end{document}